Collaborative Infrastructure for Test-Driven\\Scientific Model Validation

### 2014-03-14 sciunit-icse14/sciunit-icse14.tex
ICSE14: Final draft

While we discuss a simple example based on planetary movement here, we have applied this framework to more realistic problems in neurobiology in collaboration with a large-scale informatics project, OpenSourceBrain, whose developers are enthusiastic about developing a practical pipeline for precisely characterizing the scope and validity of the dozens of models they currently maintain (case study in preparation). The tools we describe could also be used for a variety of other scientific disciplines, including within software engineering to validate quantitative models of, for example, software cost or component reusability.

>>>>

While we discuss a simple example based on planetary movement here, we have applied this framework to more realistic problems in neurobiology in collaboration with a large-scale informatics project, OpenSourceBrain, whose developers are enthusiastic about precisely characterizing the scope and validity of the dozens of models they currently maintain (case study in preparation). The tools we describe could also be used for a variety of other scientific disciplines, including within software engineering to validate quantitative models of, for example, software cost or reusability.
